Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-12 tex/paper.tex
More images in paper
It's looking fiiiinnneeee...
Add convolution section

@@

%-------------------------------------------------------------------------
\subsection{Fully Connected Layer}

@@

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. The test accuracy was recorded every five training
iterations. An example classification of an image along with the internal state of the trained network is depicted
in Figure [?]. Figure [?] shows examples of correctly and incorrectly classified images.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}.
Again, the test accuracy was recorded every five training iterations.
An example classification of an image along with the internal state of the trained network is depicted in Figure [?].
Figure [?] shows examples of correctly and incorrectly classified images.

@@

>>>>

The convolutional layer learns a set of small filters that when convolved with the input image
during forward propagation extract salient features. This is done through the use of local 
connectivity and parameter sharing. Local connectivity refers to each unit of the convolutional 
layer being connected only to a small region of the image; this region is known as the unit’s 
receptive field, and the weights of these connections form a filter. Neighboring units in the 
convolutional layer have overlapping receptive fields, with each receptive field being shifted 
by one pixel as you move along a certain dimension. These units are then organized into feature 
maps that share the same weights on their connections. This combination of local connectivity 
and parameter sharing results in a network with sparser connectivity and fewer parameters than 
would be present in a fully connected network.

Though one could implement the convolutional layer directly by building the sparse network and 
applying the appropriate weight updates during the backpropagation step, it is also possible to 
transform this operation into the form of batch learning of the weights of a fully connected 
network (discussion in section \ref{sec:full}), such that

$$ I' \times W = [I*k_1 \hspace{10pt} I*k_2 \hspace{10pt} \cdots \hspace{10pt} I*k_K]$$
where $I$ is the image, $W$ is the weight matrix of the fully connected network, $I$’ is the transformed 
image, and $k_i$ is the $i^{\text{th}}$ kernel. The learned filters would then correspond to slices of the kernels. 
We took the later approach for ease of implementation. Figure [?] demonstrates how this transformation 
is accomplished.

@@

%-------------------------------------------------------------------------
\subsection{Fully Connected Layer}
\label{sec:full}

@@

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. The test accuracy was recorded every five training
iterations. An example classification of an image along with the internal state of the trained network is depicted
in Figure \ref{fig:actfilts}. Figure [?] shows examples of correctly and incorrectly classified images.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}.
Again, the test accuracy was recorded every five training iterations.
An example classification of an image along with the internal state of the trained network is depicted in
Figure \ref{fig:actfilts}.
Figure [?] shows examples of correctly and incorrectly classified images.

@@

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{actfilts}}
  \caption{This is also a tiger.}
  \label{fig:actfilts}
\end{figure*}
